---
output: github_document
---

# R Lille Meetup Posters <a href="https://github.com/RLille/"><img src="https://avatars1.githubusercontent.com/u/60702180" align="right" width="120" /></a>

<!-- badges: start -->
[![License](https://img.shields.io/github/license/RLille/meetup-poster)](LICENSE)
<!-- badges: end -->

```{r, echo = FALSE, message = FALSE}
source("assets/create_meetup.R")

rscript <- list.files(path = "R", pattern = "^20.*\\.R$", full.names = TRUE)
meetup <- sub("\\.R$", "", basename(rscript))
base_ads <- sapply(
  X = sprintf("meetups/%s/ads/%s", meetup, meetup),
  FUN = paste0,
  c(".png", ".md")
)

check_outdated <- function(r, a) {
  sapply(
    X = seq_along(r),
    FUN = function(i) {
      !all(sapply(a[c(i, i + 1)], file.exists)) |
        min(sapply(a[c(i, i + 1)], file.mtime)) <  max(
          sapply(
            X = c(
              r[i],
              "assets/create_meetup.R",
              "assets/poster.Rmd",
              "assets/announcement.Rmd",
              "assets/blogpost.Rmd"
            ),
            FUN = file.mtime
          )
        )
    }
  )
}
outdated <- check_outdated(rscript, base_ads)

invisible(lapply(rscript[which(outdated)], source, encoding = "UTF-8"))
```

```{r, results = "asis", echo = FALSE}
cell <- sprintf(
  paste0(
    '<td align = "center">',
      '<a href="meetups/%s/materials/README.md">',
        '<img alt="Affiche du Meetup du %s" src="%s" width="100%%" height="auto" />',
        "<br/>",
        "%s",
      "</a>",
    "</td>"
  ),
  meetup, meetup, grep("\\.png$", base_ads, value = TRUE), meetup
)
cols <- 4
rows <- ceiling(length(cell) / cols)
row_id <- rep(seq_len(rows), each = cols, length.out = length(cell))
row_cells <- split(cell, row_id)
cat("<table>\n")
cat(paste0("<tr>", sapply(row_cells, paste, collapse = ""), "</tr>"), sep = "")
cat("</table>\n")
```

*Note:* Poster/slides based on a template
by [Mickaël Canouil](https://mickael.canouil.fr/)
(<https://github.com/mcanouil/xaringan-template/>).


## Submit A Meetup Proposals

To submit a meetup proposal, make a pull request (PR) which add a new R script (in `./R`) as described below.  
The script must be named `20YY-MM-DD.R` where `YY` is the year, 
`MM` is the month and `DD` is the day of the proposed meetup.  
The PR will be reviewed, modified (if needed), and validated by the R Lille organisers.  
Once the PR is validated and merged, 
the MeetUp will be scheduled and published on [rlille.fr](https://rlille.fr)
and [meetup.rlille.fr](http://meetup.rlille.fr).

```{r, eval = FALSE, echo = TRUE}
# `R/20YY-MM-DD.R`
create_meetup(
  output = here::here("meetups/20YY-MM-DD"),
  rmd_params = list(
    title = "Title Of The Meetup", # title of the meetup
    author = "Firstname Lastname", # speaker
    institute = "", # speaker's institute/affiliation
    date = 'Thursday, the DD<sup><i style="font-size:0.5em;">th</i></sup> of MM, 20YY - 18:00 CET', # date of the meetup
    date = "20YY-MM-DD", # date of the meetup using YYYY-MM-DD format
    picture = "none", # URL of the speaker's picture, or "none"
    website = "", # URL of the speaker's website
    abstract = "", # abstract of the talk using Markdown syntax
    biography = "", # biography of the speaker using Markdown syntax
    language = "en", # language of the talk
    meetup_id = "" # to be filled by R Lille organisers
  )
)
```

*Note:* The date can be changed/updated after the PR is made.
